Multisensor Architecture for an Intersection Management System

### 2015-03-20 ch2-mdf_ims.tex
Finished table of fusion models.

In addition to models previously mentioned, there exists more proposal for data fusion architectures in literature, as can be viewed in figure \ref{fusionModelsClas}.

% TODO: Change for a table
\begin{figure}[ht!]
\centering
\includegraphics[scale=0.6]{fig/2/fusionModelsClas.png}
\caption{Classification of some data fusion models}
\label{fusionModelsClas}
\end{figure}

\begin{table}
\centering
\begin{tabular}{c c}
Category & Data Fusion Model \\

\hline
\multirow{2}{*}{Abstract Model} & Waterfall Model \cite{Harris1998} \\
& Boyd Loop \cite{Boyd1987} \\
\hline
\multirow{3}{*}{Generic Architecture} & JDL Model \cite{White1991} \\
& Multisensor Fusion Integration Model \cite{Luo1989} \\
& Omnibus model \cite{Bedworth2000} \\
\hline
\multirow{3}{*}{Rigid Architecture} & LAAS Architecture \cite{Alami1998} \\
& DFuse Architecture \cite{Kumar2003} \\
& Time-triggered Model \cite{Elmenreich2001} \\
\hline
\end{tabular}
\caption{Classification of data fusion models.}
\end{table}

>>>>

In addition to models previously mentioned, there exists more proposal for data fusion architectures in literature, as can be viewed in table \ref{fusionModelsClas}.

% TODO: Change for a table
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=0.6]{fig/2/fusionModelsClas.png}
%\caption{Classification of some data fusion models}
%\label{fusionModelsClas}
%\end{figure}

\begin{table}
\centering
\begin{tabular}{|c | c|}
\hline
\textbf{Category} & \textbf{Data Fusion Model} \\
\hline
\multirow{2}{*}{Abstract Model} & Waterfall Model \cite{Harris1998} \\
& Boyd Loop \cite{Boyd1987} \\
\hline
\multirow{3}{*}{Generic Architecture} & JDL Model \cite{White1991} \\
& Multisensor Fusion Integration Model \cite{Luo1989} \\
& Omnibus model \cite{Bedworth2000} \\
\hline
\multirow{3}{*}{Rigid Architecture} & LAAS Architecture \cite{Alami1998} \\
& DFuse Architecture \cite{Kumar2003} \\
& Time-triggered Model \cite{Elmenreich2001} \\
\hline
\end{tabular}
\caption{Classification of data fusion models}
\label{fusionModelsClas}
\end{table}
